---
title: "Network psychometrics"
author: "Rita M Ludwig & Sara J Weston"
date: "4/29/2019"
output: html_document
---

```{r setup, include=FALSE}
library('psych')
library('qgraph')
library('bootnet')
library('tidyverse')
library('dplyr')
```
Start by randomly generating some dummy data, using the names of the variables of interest from the HRS data sets. Then make the dummy data look multi-wave.
```{r dummy data gen}
set.seed(0507)

dummy = sim.multi(nvar = 68, ntrials = 3, days = 3, n.obs = 1000, plot = FALSE)
dummy$time = dummy$time/24
data = dummy %>% 
  rename(wave = time) %>% 
  select(-starts_with("F"))
```

We now have a dummy dataset of n = 1000, 68 survey items repeated over 3 waves. Now, let's get these data in the appropriate format for network analysis. Following Costantini et al. 2019, we first create a dataset where all participants' responses are meaned by variable, then a dataset where we center all variables within each participant.
```{r centering}
## For meaned dataset
mdata = data %>%
  group_by(id) %>%
  mutate_at(vars(-id,-wave), mean)

## For centered dataset
centerf = (function(x) (x - mean(x)) )

cdata = data %>%
  group_by(id) %>%
  mutate_at(vars(-id,-wave), centerf)
```
Proceed with the network psychometrics code, borrowing heavily from Costantini et al. 2019.
```{r network analysis}
## Generate correlation matrix of variables - meaned data
mcorrmat = cor(mdata[,1:68])

## Generate correlation matrix of variables - centered data
ccorrmat = cor(cdata[,1:68])

## Between-subjects network
betnetwork = EBICglasso(S = mcorrmat, n = length(unique(data$id)))
qgraph(betnetwork, layout = "spring")

## Within-subjects network
winnetwork = EBICglasso(S = ccorrmat, n = nrow(data)) 
qgraph(winnetwork, layout = "spring")
```
Now some output statistics. Again, code copied or adapted from Constantini et al. 2019.
```{r network analysis output statistics}
# The following code computes the correlation stability coefficients for centrality estimates. Notice that this computation may take a while.
nboots = 10000
caseN = 100
btnt <- list()
# bootnet on the between-subject network
set.seed(1)
btnt$betnetwork <- bootnet(select(mdata, -c(wave, id)),
                         default = "EBICglasso",
                         type = "case",
                         nBoots = nboots,
                         caseN = caseN)

# bootnet on the within-subject network
set.seed(1)
btnt$winnetwork <- bootnet(select(cdata, -c(wave, id)),
                         default = "EBICglasso",
                         type = "case",
                         nBoots = nboots,
                         caseN = caseN)
corStability(btnt$betnetwork)
corStability(btnt$winnetwork)

### Centrality and clustering coefficient estimates
centrality_auto(betnetwork)
centralityPlot(betnetwork)
clustcoef_auto(betnetwork)
clusteringPlot(betnetwork, include = "Zhang", signed = TRUE)

centrality_auto(winnetwork)
centralityPlot(winnetwork)
clustcoef_auto(winnetwork)
clusteringPlot(winnetwork, include = "Zhang", signed = TRUE)
```